---
title: RNA Repair
author: Jay Hesselberth
date: '2017-08-18'
slug: rna-repair
categories: []
tags:
  - Repair
image_preview: "hex/rna-hex.svg"
header:
  image: "hex/rna-hex.svg"
---

We use genetics, biochemistry and cell biology to understand how and why cells repair RNA transcripts.

## tRNA splicing

```{r, echo = FALSE}
htmltools::img(src = "/img/figure/trna-block.svg",
               alt = "tRNA figure",
               style = 'float: right; margin: 0px 0px 15px 15px;')
```

We exploited a previously developed strategy to bypass the essential function of RNA repair enzymes in budding yeast. Cells that express "pre-spliced" tRNAs are viable in the absence of the tRNA ligase and 2´-phosphotransferase. We are using these cells to understand tRNA processing and translational fidelity.

## Unfolded protein response

```{r, echo = FALSE}
htmltools::img(src = "/img/figure/upr.svg",
               alt = "UPR figure",
               style = 'float: right; margin: 0px 0px 15px 15px;')
```

We exploited a previously developed strategy to bypass the essential function of RNA repair enzymes in budding yeast. Cells that express "pre-spliced" tRNAs are viable in the absence of the tRNA ligase and 2´-phosphotransferase. We are using these cells to understand tRNA processing and translational fidelity.

We exploited a previously developed strategy to bypass the essential function of RNA repair enzymes in budding yeast. Cells that express "pre-spliced" tRNAs are viable in the absence of the tRNA ligase and 2´-phosphotransferase. We are using these cells to understand tRNA processing and translational fidelity.

## New substrates of RNA repair

We are conducting targeted and genome-wide searches for other targets of RNA repair. Such studies could provide new insights into the role of RNA repair in cellular physiology.

## Funding

This work is funded by an NIH MIRA grant (R35 GM119550).